---
title: "Map"
author: "Pedram Hash"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## fars_read

```{r, echo = FALSE, include=FALSE}
library(magrittr)
library(dplyr)
library(maps)
library(graphics)
source('../R/make_filename.R')
source('../R/fars_read_years.R')
source('../R/fars_summerize_years.R')
source('../R/fars_map_state.R')
# source('../data')
# source('../Data/accident_2014.csv.bz2')
# source('../Data/accident_2015.csv.bz2')
```

The function `fars_read()` takes as argument the name of a file and reads it into R. if the function does not exist it will return an error: "The file does not exist".
```{r, eval=FALSE}
data_2013 <- fars_read('accident_2013.csv.bz2')

```
One way to use this function is to enter the file name manually. However since we use specific files with generic format "accident_YYYY.csv.bz2". All we need to do is to replace the YYYY with a four digit year. This can be done with the function `make_filename()` and passing the four-digit year as argument.

```{r}
filename = make_filename(2013)
print(filename)
```
Instead of reading files one by one you can use the function `fars_read_years()` and passing in a vector of years. Then the function will return a list of the table where each element contains the data from a file.

```{r, eval=FALSE}
tbl <- fars_read_years(c(2013, 2014, 2015))
```

### Summary Table

the function `fars_summerize_years()` takes a vector of years and calls `fars_read_years()` with the vector of years. it does a row binding over all the tbls it groups the yielded tibble by year and MONTH and then counts the occurances and then it makes a wide tibble from the long tibble according to year.

```{r eval=FALSE}
summary_tbl <- fars_summerize_years(c(2013, 2014, 2015))
print(summary_tbl)
```
## fars_map_state

By calling this function you can get the map of accidents in a year and a state in US. You can get this map by inputing a state number and a year.
```{r, eval=FALSE}
fars_map_state(10, 2013)
```




